### 2010-12-09 doc/tech_doc/a-rex/arex_tech_doc.tex
Modified code and documentation about (semi-)static information published by AREX. By default this feature is disable.

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/arcconfig/2009/08"
  xmlns:loader="http://www.nordugrid.org/schemas/loader/2009/08"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/2009/08"
  xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
  xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
  xmlns:authz="http://www.nordugrid.org/schemas/arcauthz/2009/08"
  xmlns:idmap="http://www.nordugrid.org/schemas/identitymap/2009/10"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arc/arched.log</File>
      <MaxSize>100000000</MaxSize>
      <Backups>10</Backups>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <loader:ModuleManager>
    <loader:Path>/usr/local/lib/arc/</loader:Path>
  </loader:ModuleManager>
  <!-- Simply load all needed plugins -->
  <loader:Plugins>
    <loader:Name>mcctcp</loader:Name>
    <loader:Name>mcctls</loader:Name>
    <loader:Name>mcchttp</loader:Name>
    <loader:Name>mccsoap</loader:Name>
    <loader:Name>arcpdc</loader:Name>
    <loader:Name>identitymap</loader:Name>
    <loader:Name>arex</loader:Name>
  </loader:Plugins>
  <!-- Create a chain -->
  <loader:Chain>
    <!-- TCP listening socket -->
    <loader:Component name="tcp.service" id="tcp">
      <loader:next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </loader:Component>
    <!-- Transport-level security -->
    <loader:Component name="tls.service" id="tls">
      <loader:next id="http"/>
      <!-- Location of server's security keys -->
      <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
      <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
      <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
      <loader:SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>
      </loader:SecHandler>
    </loader:Component>
    <!-- HTTP processing is done here -->
    <loader:Component name="http.service" id="http">
      <loader:next id="soap">POST</loader:next>
      <loader:next id="plexer">GET</loader:next>
      <loader:next id="plexer">PUT</loader:next>
    </loader:Component>
    <!-- This one parses content into XML tree -->
    <loader:Component name="soap.service" id="soap">
      <loader:next id="plexer"/>
    </loader:Component>
    <!-- Directing messages to proper service -->
    <loader:Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
      Unmatched part of path is propagated to service in
      PLEXER:EXTENSION attribute. -->
      <loader:next id="a-rex">^/arex</loader:next>
    </loader:Plexer>
    <!-- A-Rex service -->
    <loader:Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
      Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </loader:Service>
  </loader:Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

@@

\begin{footnotesize}
\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
xmlns:xsd="http://www.w3.org/2001/XMLSchema"
xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
xmlns:arc="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
targetNamespace="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
elementFormDefault="qualified">
  <xsd:complexType name="endpoint_Type">
    <!--
    This element defines URL of A-REX service as seen from outside.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string"> 
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="endpoint" type="endpoint_Type"/>
  <xsd:complexType name="gmconfig_Type">
    <!--
    This element defines path to arc0 Grid Manager configuartion file.
    By default it is /etc/arc.conf.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string">
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="gmconfig" type="gmconfig_Type"/>
  <xsd:simpleType name="gmrun_Type">
    <!--
    This element defines how grid-manager part of A-Rex is run.
    {*} internal - as a thread inside service container.
    {*} none - no grid-manager is run.
    {*} external - as a separate executable (not supported anymore).
    Default is 'internal'.
    -->
    <xsd:restriction base="xsd:string">
      <xsd:enumeration value="internal"/>
      <xsd:enumeration value="external"/>
      <xsd:enumeration value="none"/>
    </xsd:restriction>
  </xsd:simpleType>
  <xsd:element name="gmrun" type="gmrun_Type"/>
  <xsd:complexType name="usermap_Type">
    <xsd:sequence>
      <xsd:element name="defaultLocalName" type="xsd:string"
                   minOccurs="0"/>
    </xsd:sequence>
  </xsd:complexType>
  <xsd:element name="usermap" type="usermap_Type"/>
  <!-- CommonName attribute of bes-factory. -->
  <xsd:element name="commonName" type="xsd:string"/>
  <!-- LongDescription attribute of bes-factory. -->
  <xsd:element name="longDescription" type="xsd:string"/>
  <!-- Name of Local Resource Management System. -->
  <xsd:element name="LRMSName" type="xsd:string"/>
  <!--
  Name of Operating System.
  The values are based on the OSType field of the CIM_OperatingSystem model:
  http://www.dmtf.org/standards/cim/cim_schema_v29
  -->
  <xsd:element name="OperatingSystem" type="xsd:string"/>
</xsd:schema>
\end{verbatim}
\end{footnotesize}

>>>>

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/arcconfig/2009/08"
  xmlns:loader="http://www.nordugrid.org/schemas/loader/2009/08"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/2009/08"
  xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
  xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
  xmlns:authz="http://www.nordugrid.org/schemas/arcauthz/2009/08"
  xmlns:idmap="http://www.nordugrid.org/schemas/identitymap/2009/10"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arc/arched.log</File>
      <MaxSize>100000000</MaxSize>
      <Backups>10</Backups>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <loader:ModuleManager>
    <loader:Path>/usr/local/lib/arc/</loader:Path>
  </loader:ModuleManager>
  <!-- Simply load all needed plugins -->
  <loader:Plugins>
    <loader:Name>mcctcp</loader:Name>
    <loader:Name>mcctls</loader:Name>
    <loader:Name>mcchttp</loader:Name>
    <loader:Name>mccsoap</loader:Name>
    <loader:Name>arcpdc</loader:Name>
    <loader:Name>identitymap</loader:Name>
    <loader:Name>arex</loader:Name>
  </loader:Plugins>
  <!-- Create a chain -->
  <loader:Chain>
    <!-- TCP listening socket -->
    <loader:Component name="tcp.service" id="tcp">
      <loader:next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </loader:Component>
    <!-- Transport-level security -->
    <loader:Component name="tls.service" id="tls">
      <loader:next id="http"/>
      <!-- Location of server's security keys -->
      <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
      <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
      <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
      <loader:SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>
      </loader:SecHandler>
    </loader:Component>
    <!-- HTTP processing is done here -->
    <loader:Component name="http.service" id="http">
      <loader:next id="soap">POST</loader:next>
      <loader:next id="plexer">GET</loader:next>
      <loader:next id="plexer">PUT</loader:next>
    </loader:Component>
    <!-- This one parses content into XML tree -->
    <loader:Component name="soap.service" id="soap">
      <loader:next id="plexer"/>
    </loader:Component>
    <!-- Directing messages to proper service -->
    <loader:Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
      Unmatched part of path is propagated to service in
      PLEXER:EXTENSION attribute. -->
      <loader:next id="a-rex">^/arex</loader:next>
    </loader:Plexer>
    <!-- A-Rex service -->
    <loader:Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
      Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
      <!-- This optional parameter can be used to enable publishing of additional
      information to ISIS. The default is not to publish ("no"). The information,
      which is considered in some degree to be static, includes HealthState, 
      OSFamily, Platform, PhysicalCPUs, CPUMultiplicity, CPUModel and
      ApplicationEnvironment.--> 
      <arex:publishStaticInfo>yes<arex:publishStaticInfo>

    </loader:Service>
  </loader:Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

@@

\begin{footnotesize}
\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<xsd:schema
xmlns:xsd="http://www.w3.org/2001/XMLSchema"
xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
xmlns:arc="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
targetNamespace="http://www.nordugrid.org/schemas/ArcConfig/2007/arex"
elementFormDefault="qualified">
  <xsd:complexType name="endpoint_Type">
    <!--
    This element defines URL of A-REX service as seen from outside.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string"> 
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="endpoint" type="endpoint_Type"/>
  <xsd:complexType name="gmconfig_Type">
    <!--
    This element defines path to arc0 Grid Manager configuartion file.
    By default it is /etc/arc.conf.
    -->
    <xsd:simpleContent>
      <xsd:extension base="xsd:string">
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>
  <xsd:element name="gmconfig" type="gmconfig_Type"/>
  <xsd:simpleType name="gmrun_Type">
    <!--
    This element defines how grid-manager part of A-Rex is run.
    {*} internal - as a thread inside service container.
    {*} none - no grid-manager is run.
    {*} external - as a separate executable (not supported anymore).
    Default is 'internal'.
    -->
    <xsd:restriction base="xsd:string">
      <xsd:enumeration value="internal"/>
      <xsd:enumeration value="external"/>
      <xsd:enumeration value="none"/>
    </xsd:restriction>
  </xsd:simpleType>
  <xsd:element name="gmrun" type="gmrun_Type"/>
  <xsd:complexType name="usermap_Type">
    <xsd:sequence>
      <xsd:element name="defaultLocalName" type="xsd:string"
                   minOccurs="0"/>
    </xsd:sequence>
  </xsd:complexType>
  <xsd:element name="usermap" type="usermap_Type"/>
  <!-- CommonName attribute of bes-factory. -->
  <xsd:element name="commonName" type="xsd:string"/>
  <!-- LongDescription attribute of bes-factory. -->
  <xsd:element name="longDescription" type="xsd:string"/>
  <!-- Name of Local Resource Management System. -->
  <xsd:element name="LRMSName" type="xsd:string"/>
  <!--
  Name of Operating System.
  The values are based on the OSType field of the CIM_OperatingSystem model:
  http://www.dmtf.org/standards/cim/cim_schema_v29
  -->
  <xsd:element name="OperatingSystem" type="xsd:string"/>
  <!--
  Optional parameter which is enable to publish additional
  information to ISIS. 
  {*} yes - Allow publishing additional information.
  {*} no  - Disallow additional information to publish. 
            Registered with Only contact information.  
  -->  
    <xsd:element name="publishStaticInfo" default="no">
      <xsd:simpleType>
        <xsd:annotation>
          <xsd:documentation xml:lang="en">
            This optional parameter can be used to enable publishing
            of additional information to ISIS. The default is not to
            publish ("no"). The information, which is considered in
            some degree to be static, includes HealthState, OSFamily,
            Platform, PhysicalCPUs, CPUMultiplicity, CPUModel and
            ApplicationEnvironment.
          </xsd:documentation>
        </xsd:annotation>
        <xsd:restriction base="xsd:string">
          <xsd:enumeration value="no">
          <xsd:enumeration value="yes">
        </xsd:restriction>
      </xsd:simpleType>
    </xsd:element>

</xsd:schema>
\end{verbatim}
\end{footnotesize}
